### 2020-12-22 paper/localpsf.tex
organizing paper more

\subsection{Connection to existing work}

@@

\subsection{Background: hierarchical matrices}

\section{Choosing sample points}
\label{sec:choosing_sample_points}

We extract $\varphi_{x_i}$ for many points $x_i$ by applying $\mathcal{A}$ to Dirac combs associated with ``batches'' of points. In this section we describe how we choose the points $x_i$. The challenge is to choose as many points as possible per batch, while ensuring that the points in each batch are not too close to each other, and are not too close to $\partial \Omega$.

Ensuring that the points $x_i$ are well separated from each other requires estimating the supports of the functions $\langle\mathcal{A},\delta_{x}\rangle^*$. Since $\varphi_x$, and thus $\langle\mathcal{A},\delta_{x}\rangle^*$, is nonnegative, $\langle\mathcal{A},\delta_{x}\rangle^*$ is a scaled probability distribution. We compute the scaling factors for all $x$ simultaneously by applying $\mathcal{A}$ to a constant function. We then compute the mean and covariance of the normalized version of $\langle\mathcal{A},\delta_{x}\rangle^*$, for all $x$ simultaneously, by applying $\mathcal{A}^T$ to a small number of linear and quadratic functions. The support of $\langle\mathcal{A},\delta_{x}\rangle^*$ is estimated to be contained in an ellipsoid of points that are within a small number of standard deviations of the mean for a Gaussian distribution with the same mean and covariance as the normalized version of $\langle\mathcal{A},\delta_{x}\rangle^*$.

The function $\varphi_x(y)$ is undefined when $x + y \notin \Omega$, which can occur even if $x \in \Omega$ and $y \in \Omega$. Extending $\varphi_x$ by zero makes it defined for all $y \in \mathbb{R}^d$, but this extension is only reasonable if $x$ is far enough from $\partial \Omega$ that $\varphi_x(y)$ decays to zero, as a function of $y$, before $y$ reaches $\partial \Omega$. We therefore choose exclude sample points $x_i$ if the ellipsoid associated with that point overlaps the boundary.

@@

\subsection{Greedy point selection algorithm}
\label{sec:greedy_point_selection}

@@

We select a batch of sample points, $S_b$, randomly from a finite set of candidate points $P$. Starting from an empty set, we build $S_b$ by choosing candidate points $p$ from $P$, one at a time. The current candidate point, $p$, is the point in $P$ that is the farthest away from all points in previous sample point baches. That is, the minimizer of the following optimization problem:
\begin{equation*}
\min_{p \in P} \max_{x \in S_1 \cup \dots \cup S_{b-1}} \|p - x\|
\end{equation*}
After we choose the candidate $p$, we remove $p$ from $P$.
If $p$ is sufficiently far from all of the previously chosen points in the current batch, in the sense that $E_p \cap E_q = \{\}$ for all $q \in S_b$, and if $p$ is sufficiently far from the boundary, in the sense that $E_p \cap \partial \Omega = \{\}$, then we add $p$ to $S_b$. Otherwise we discard $p$. This process repeats until it is no longer possible to pick a point from $P$ that is sufficiently far from the points in $S_b$. 
%This is detailed in Algorithm \ref{alg:point_choice}.

We repeat the process to construct several batches of points $S_1, S_2, \dots$, until the total number of sample points exceeds a desired threshold. In our implementation, the set of candidate points $P$ is the set of all Lagrange nodes for the finite element basis functions $\phi_i$ used to discretize the problem, minus all points in previously chosen batches.

@@

	Start with a finite set of candidate points $P \subset \Omega_I$

@@

\subsection{Extracting impulse responses at sample points}
\label{sec:get_impulse_response}

@@

\section{Discretized algorithms}

@@

\section{Additional proofs}
\label{app:proofs}

>>>>

\subsection{Existing work}

@@

\section{Constructing the approximation}
\label{sec:method}
This section describes how we compute the convolution kernels, $\varphi_i$, and weighting functions, $w_i$, for the product-convolution approximation, $\widetilde{\mathcal{A}} \approx \mathcal{A}$, given by
\begin{equation}
\left(\widetilde{\mathcal{A}}u\right)(v) := \left( v,~ \sum_{i=1}^r \varphi_i \ast \left(w_i \cdot u\right) \right)_{L^2(\Omega)}.
\end{equation}

We extract $\varphi_{x_i}$ for many points $x_i$ by applying $\mathcal{A}$ to Dirac combs associated with ``batches'' of points (Section \ref{sec:get_impulse_response}). We use a greedy algorithm to choose as many points as possible per batch, while ensuring that the points in each batch are not too close to each other, and are not too close to $\partial \Omega$ (Section \ref{sec:greedy_point_selection}).

Ensuring that the points $x_i$ are well separated from each other requires estimating the supports of the functions $\langle\mathcal{A},\delta_{x}\rangle^*$ (Section \ref{eq:mean_and_covariance_estimation}). Since $\varphi_x$, and thus $\langle\mathcal{A},\delta_{x}\rangle^*$, is nonnegative, $\langle\mathcal{A},\delta_{x}\rangle^*$ is a scaled probability distribution. We compute the scaling factors for all $x$ simultaneously by applying $\mathcal{A}$ to a constant function. We then compute the mean and covariance of the normalized version of $\langle\mathcal{A},\delta_{x}\rangle^*$, for all $x$ simultaneously, by applying $\mathcal{A}^T$ to a small number of linear and quadratic functions. The support of $\langle\mathcal{A},\delta_{x}\rangle^*$ is estimated to be contained in an ellipsoid of points that are within a small number of standard deviations of the mean for a Gaussian distribution with the same mean and covariance as the normalized version of $\langle\mathcal{A},\delta_{x}\rangle^*$.

%The function $\varphi_x(y)$ is undefined when $x + y \notin \Omega$, which can occur even if $x \in \Omega$ and $y \in \Omega$. Extending $\varphi_x$ by zero makes it defined for all $y \in \mathbb{R}^d$, but this extension is only reasonable if $x$ is far enough from $\partial \Omega$ that $\varphi_x(y)$ decays to zero, as a function of $y$, before $y$ reaches $\partial \Omega$. We therefore choose exclude sample points $x_i$ if the ellipsoid associated with that point overlaps the boundary.

@@

\subsection{Greedy sample point selection}
\label{sec:greedy_point_selection}

@@

We select a batch of sample points, $S_b$, randomly from a finite set of candidate points $P$. Starting from an empty set, we build $S_b$ by choosing candidate points $p$ from $P$, one at a time. The current candidate point, $p$, is the point in $P$ that is the farthest away from all points in previous sample point baches. That is, the maximizer of the following optimization problem:
\begin{equation*}
\max_{p \in P} \min_{x \in S_1 \cup \dots \cup S_{b-1}} \|p - x\|
\end{equation*}
After we choose the candidate $p$, we remove $p$ from $P$.
If $p$ is sufficiently far from all of the previously chosen points in the current batch, in the sense that $E_p \cap E_q = \{\}$ for all $q \in S_b$, and if $p$ is sufficiently far from the boundary, in the sense that $E_p \cap \partial \Omega = \{\}$, then we add $p$ to $S_b$. Otherwise we discard $p$. This process repeats until there are no more points in $P$. 
%This is detailed in Algorithm \ref{alg:point_choice}.

We repeat the process to construct several batches of points $S_1, S_2, \dots$, until the total number of sample points exceeds a desired threshold. In our implementation, the set of candidate points $P$ is the set of all Lagrange nodes for the finite element basis functions used to discretize the problem, minus all points in previously chosen batches.

@@

	Start with a finite set of candidate points $P \subset \Omega$

@@

\subsection{Batched computation of impulse responses}
\label{sec:get_impulse_response}

@@

@@

\section{Additional theory}
\label{app:proofs}
